\newgeometry{bottom=0.1cm, top=0.1cm, left=0.1cm, right=0.1cm}
\begin{landscape}
\captionsetup{width=1\textwidth}
\thispagestyle{empty}
\renewcommand{\arraystretch}{1.5}
\section*{Table of primitives}
\begin{longtable}[c]{ c  p{7cm}  c  c  c  c  p{3cm}  c  c }
\caption{This table presents a list of the different cryptographic primitives that are being used in IOHK, or primitives that are being worked on. We divide the status in four groups: \InProduction, \Testing, \Developing, \Deprecated, to represent primitives used in production, being tested or audited, being under development, or deprecated respectively.\label{table:crypto-primitives}}\\

 \hline
 \multicolumn{9}{ c }{List of cryptographic primitives}\\
 \hline
 Name & \centering Protocol & Language & Tech. Details & Project & Status & Provider & Internal Contact & Plutus support\\ 
 \hline
 \endfirsthead

 \hline
 \multicolumn{9}{c}{Continuation of Table \ref{table:crypto-primitives}}\\
 \hline
Name & \centering Protocol & Language & Tech. Details & Project & Status & Provider & Internal Contact & Plutus support \\
 \hline
 \endhead

 \hline
 \endfoot

 \hline
 \multicolumn{9}{ c }{}\\%End of Table}\\
 \hline\hline
 \endlastfoot
 
ed25519 & EdDSA implemented over Curve25519. & \href{https://github.com/jedisct1/libsodium/tree/master/src/libsodium/crypto_sign/ed25519}{C} & Section~\ref{sec:ed25519} & Cardano node & \InProduction & libsodium & & Yes\\
%
\hdashline
%
KES & Key Evolving Signatures. Implemented on top of a digital signature scheme, in particular ed25519. Haskell implementation depends on libsodium. & \href{https://github.com/input-output-hk/cardano-base/tree/master/cardano-crypto-class/src/Cardano/Crypto/KES}{Haskell}  & Section~\ref{sec:kes} & Cardano node & \InProduction & IOHK (based on libsodium) &  & Yes \\
% 
& & \href{https://github.com/input-output-hk/chain-libs/tree/master/chain-crypto/src/algorithms/sumed25519}{Rust} & & Jormungandr & \InProduction  & IOHK & & \\
%
\hdashline
%
MuSig2 & Schnorr-based multi signatures. In particular, this implementation is compatible with ed25519 signatures. & \href{https://github.com/input-output-hk/musig2}{C} & Section~\ref{sec:musig2} & Hydra & \Developing & IOHK (based on libsodium) & & Yes\\
%
\hdashline
%
STM & Stake-based Threshold Multi signatures. This construction depends on a pairing friendly curve. & \href{https://github.com/input-output-hk/mithril}{Rust} & Section~\ref{sec:stm} & Mithril & \Developing & IOHK/Galois & & No \\ 
%
\hdashline
%
ATM & Ad-hoc Threshold Multi signatures. Achieves the same goal as Threshold Signatures, with the difference that the key generation does not require a distributed procedure. Each party generates their key pair, and then a global public key is computed. & \href{https://github.com/input-output-hk/mithril}{Rust} & Section~\ref{sec:atm} & Side chains & \Developing & IOHK/Galois & & No\\ 
%
\hdashline
%
 VRF & Verifiable Random Function, implemented over Curve25519. & \href{https://github.com/input-output-hk/libsodium/tree/draft-irtf-cfrg-vrf-03/src/libsodium/crypto_vrf}{C} & Section~\ref{sec:vrf} & Cardano node & \InProduction & IOHK & & -\\
 %
& & \href{https://github.com/input-output-hk/chain-libs/tree/master/chain-crypto/src/algorithms/vrf}{Rust} & & Jormungandr & \InProduction & IOHK &  \\
%
\hdashline
%
Plonk & zk-SNARK. No generic computation available yet, restricted to the gadgets implemented. & \href{https://github.com/ZK-Garage/plonk}{Rust} & Section~\ref{sec:plonk} & Midnight & \Developing & ZK-Garage & & No
 \end{longtable}
\end{landscape}
\restoregeometry
